---
title: "Platt1980 Model Opt"
author: "MLB"
date: "2024-08-01"
output: html_document
---

# Load FRRf files

## Step 1: Load in TBK's TheSource Functions for FRRf data files

```{r}

## Functions for analyzing FRRF Output
##
## Author: Thomas Bryce Kelly (tkelly@alaska.edu)
## http://about.tkelly.org/
##
## College of Fisheries and Ocean Sciences
## University of Alaska Fairbanks
##
## Dept of Earth, Ocean & Atmospheric Sciences
## Florida State University



#' @title Load FRRF Datafiles
#' @author Thomas Bryce Kelly
#' @param input.dir the input directory
#' @param files.names the name of the file in the input directory (default will load all files in that directory)
#' @export
load.frrf = function(input.dir, file.names = NULL, verbose = T) {
    if (is.null(file.names)) {
        if (verbose) { message('No files provided, attempting to load all files in target directory.')}
        file.names = list.files(input.dir, pattern = '*.csv')
    }

    if (verbose) { message('Preparing to load ', length(file.names), ' files.')}
    result = list()

    for (file.name in file.names) {

        if (verbose) { message('Loading ', paste0(input.dir, file.name), appendLF = F)}

        con = file(paste0(input.dir, file.name), "r")

        col.names = c('Saq', 'E', 'Start', 's', 'Chl', 'ADC', 'rP.obs', 'rP.fit', 'JPII', 'JVPII', 'Fo', 'Fm', 'Fv.Fm',
                      'C', 'p', 'RSigma', 'Sigma', 'CSQ', 'TauES', 'NPQ', 'NSV', 'QR', 'Qo', 'Qm', 'Qo.SE', 'Qm.SE',
                      'Q.SE', 'Q.SE.ratio', 'Qo.points', 'Qo.slope', 'Qo.int', 'Qm.points', 'Qm.slope', 'Qm.int')

        data.a = data.frame(Saq = NA, E = NA, Start = NA, s = NA, Chl = NA, ADC = NA,
                            rP.obs = NA, rP.fit = NA, JPII = NA, JVPII = NA, Fo = NA,
                            Fm = NA, Fv.Fm = NA, C = NA, p = NA, RSigma = NA, Sigma = NA, CSQ = NA,
                            TauES = NA, NPQ = NA, NSV = NA, QR = NA, Qo = NA, Qm = NA,
                            Qo.SE = NA, Qm.SE = NA, Q.SE = NA, Q.SE.ratio = NA, Qo.points = NA,
                            Qo.slope = NA, Qo.int = NA, Qm.points = NA, Qm.slope = NA, QM.int = NA)

        data.b = data.a
        data.c = data.a
        data.d = data.a

        data.s = data.frame(LED = c('A','B','C','D'), Alpha = NA, Ek = NA, Pm = NA, Em = NA, AlphaW = NA, SErP = NA,
                            nPSII = NA, RCII = NA, stringsAsFactors = FALSE)

        parms = data.frame(Ka = NA, Chl.multiplier = NA, QR.threshold = NA, C.derivation = NA, Tau.PQ = NA, Tau.SQ = NA)
        suppressWarnings({
            while (TRUE) {
                ## Load file line by line
                line = readLines(con, n = 1)
                if (length(line) == 0) {
                    break
                }
                line = strsplit(line, split = ',')[[1]]

                if (length(line) > 1) {
                    ## Check for PARAM values
                    if (line[1] == 'FRRf3 Ka:') {
                        parms$Ka = as.numeric(line[2])
                    }
                    else if (line[1] == '[Chl] multiplier:') {
                        parms$Chl.multiplier = as.numeric(line[2])
                    }
                    else if (line[1] == 'QR threshold:') {
                        parms$QR.threshold = line[2]
                    }
                    else if (line[1] == 'C derivation:') {
                        parms$C.derivation = line[2]
                    }
                    else if (line[1] == 'TauPQ:') {
                        parms$Tau.PQ = as.numeric(line[2])
                    }
                    else if (line[1] == 'TauSQ:') {
                        parms$Tau.SQ = as.numeric(line[2])
                    }


                    else if (line[1] == 'Alpha:') {
                        data.s$Alpha = as.numeric(line[2:5])
                    }
                    else if (line[1] == 'Ek:') {
                        data.s$Ek = as.numeric(line[2:5])
                    }
                    else if (line[1] == 'Pm:') {
                        data.s$Pm = as.numeric(line[2:5])
                    }
                    else if (line[1] == 'Em:') {
                        data.s$Em = as.numeric(line[2:5])
                    }
                    else if (line[1] == 'AlphaW:') {
                        data.s$AlphaW = as.numeric(line[2:5])
                    }
                    else if (line[1] == 'SErP:') {
                        data.s$SErP = as.numeric(line[2:5])
                    }

                    ## Data A Values
                    else if (length(line) > 1 & line[2] == 'LED combination A (450 nm alone)') {
                        line = readLines(con, n = 1) ## Next line
                        while (TRUE) {
                            line = readLines(con, n = 1) ## Next line
                            if (length(line) == 0) {
                                break
                            }
                            line = as.numeric(strsplit(line, split = ',')[[1]])

                            if (is.na(line[2])) {
                                break
                            }
                            if (line[2] > 0 & line[2] < 25) {
                                data.a[line[2],] = line[c(2:22,24:30,32:37)]
                            }

                        }
                    }

                    ## Data B Values
                    else if (length(line) > 1 & line[2] == 'LED combination B (450 + 530 nm)') {
                        line = readLines(con, n = 1) ## Next line
                        while (TRUE) {
                            line = readLines(con, n = 1) ## Next line
                            if (length(line) == 0) {
                                break
                            }
                            line = as.numeric(strsplit(line, split = ',')[[1]])

                            if (is.na(line[2])) {
                                break
                            }
                            if (length(line) > 1 & line[2] > 0 & line[2] < 25) {
                                data.b[line[2],] = line[c(2:22,24:30,32:37)]
                            }

                        }
                    }

                    ## Data C Values
                    else if (length(line) > 1 & line[2] == 'LED combination C (450 + 624 nm)') {
                        line = readLines(con, n = 1) ## Next line
                        while (TRUE) {
                            line = readLines(con, n = 1) ## Next line
                            if (length(line) == 0) {
                                break
                            }
                            line = as.numeric(strsplit(line, split = ',')[[1]])

                            if (is.na(line[2])) {
                                break
                            }
                            if (line[2] > 0 & line[2] < 25) {
                                data.c[line[2],] = line[c(2:22,24:30,32:37)]
                            }

                        }
                    }

                    ## Data D Values
                    else if (length(line) > 1 & line[2] == 'LED combination D (450 + 530 + 624 nm)') {
                        line = readLines(con, n = 1) ## Next line
                        while (TRUE) {
                            line = readLines(con, n = 1) ## Next line
                            if (length(line) == 0) {
                                break
                            }
                            line = as.numeric(strsplit(line, split = ',')[[1]])

                            if (length(line) > 1 & is.na(line[2])) {
                                break
                            }
                            if (length(line) > 1 & line[2] > 0 & line[2] < 25) {
                                data.d[line[2],] = line[c(2:22,24:30,32:37)]
                            }

                        }
                    }

                }
            }
            if (verbose) { message('... Success.')}
        })

        close(con)

        ## Generate Datetime stamp:

        datetime = tryCatch(
            {
                year = substr(file.name, 1, 4)
                month = substr(file.name, 5, 6)
                day = substr(file.name, 7, 8)
                hour = substr(file.name, 10, 11)
                minute = substr(file.name, 12, 13)
                second = substr(file.name, 14, 15)

                as.POSIXct(paste0(year, '-', month, '-', day, ' ', hour, ':', minute, ':', second), tz = 'UTC')
            },
            error = function(c) {
                NA
            }
        )
        if (!is.na(datetime)) {
        result[[paste0('Y', year, month, day, hour, minute, second)]] = list(Params = parms, S = data.s,
                                                                             A = data.a, B = data.b, C = data.c, D = data.d,
                                                                             Datetime = datetime, File = paste0(file.name))
        } else {
            result[[file.name]] = list(Params = parms, S = data.s,
                                                                                 A = data.a, B = data.b, C = data.c, D = data.d,
                                                                                 Datetime = datetime, File = paste0(file.name))
        }
    }

    result$meta = list(
        # Source.version = packageVersion('TheSource'),
        R.version = R.version.string
    )
    ## Return
    result
}


#' @title Webb 1974 Light Curve
#' @param alpha the initial slope of the P vs E curve
#' @param Ek a light saturation parameter
#' @param E the photosynthetically active radiation
#' @export
model.Webb1974 = function(alpha, Ek, E) {
    alpha * Ek * (1 - exp(-E/Ek))
}


#' @title Platt 1980 Light Curve
#' @export
#' @inheritParams model.Webb1974
model.Platt1980 = function(alpha, beta, Ps, E) {
    Ps * (1 - exp(-1 * alpha * E / Ps)) * exp(-beta * E / Ps)
}


#' @title Jassby 1976 Light Model
#' @export
#' @inheritParams model.Webb1974
model.Jassby1976 = function(alpha, Ek, E) {
    alpha * Ek * tanh(E / Ek)
}


#' @title Eilers 1988 Light Model
#' @export
#' @inheritParams model.Webb1974
model.Eilers1988 = function(alpha, Eopt, Pm, E) {
    a = 1 / (alpha * Eopt^2)
    b = 1 / Pm - 2 / (alpha * Eopt)
    c = 1/ alpha

    E / (a * E^2 + b * E + c)
} #there is a beta term in here - the w term. inhibition term stuff
# w = b/sqrt(a*c). in teh results section, plug abc into equation to calc w?

#' @title Which Closest Time
#' @description  Find the indicies of the closest times for each entry of x
#' @export
which.closest.time = function(x, y) {
  if (length(y) > 1) {
    l = rep(NA, length(x))
    for (i in 1:length(x)) {
      l[i] = which.min(as.numeric(difftime(x[i], y, units='mins'))^2)
    }
  } else {
    l = which.min(as.numeric(difftime(x, y, units='mins'))^2)
  }
  l
}

#' @title Parameter Search
#' @author Thomas Bryce Kelly
#' @description Implements a recursive grid search routine to solve optimization problems in arbitrary dimensions.
#' @param n Number of recursions to perform
#' @param cost The cost function which must return a numeric value and accept parameter values as the first arguments and in the order they are provided.
#' @param ... Optional argument that is passed directly onto the cost function
#' @param bounds A dataframe containing the minimum and maximum values permitted of each parameter
#' @param splits The number of subdivisions to perform for each dimension (so grid size is n x splits ^ dimensionality)
#' @param progression The size of the new search-space to interrogate. A value between 1 and splits/2. Default value (NULL) will yeield a progression of max(1, splits/4), good for most problems.
#' @export
parameter.search = function(n, cost, grid = NULL, bounds, splits = 10, progression = NULL, verbose = T, ...) {

  if (verbose){
    message('Starting Parameter Search')
    message('Parameter search is an iterative grid search algorithm that seeks the parameters that minimize\nan objective cost function given a set of parameter bounds.')
  }

  ## Init Timer
  a = Sys.time()

  if (splits <= 2) { stop('splits argument must be an integer greater than or equal to 3!')}
  if(is.null(progression)) {
    progression = max(1, ceiling(splits / 4))
    if (verbose) { message(' No Progresssion given, default to:\t', progression) }
  }

  splits = round(splits)
  if (verbose) {message(' Number of splits set to:\t\t', splits)}
  ## How many dimensions
  dim = nrow(bounds)

  ## Setup search grid
  b = list()
  for (i in 1:nrow(bounds)) {
    if (bounds[i,1] == bounds[i,2]) {
      b[[i]] = bounds[i,1]
    } else {
      b[[i]] = seq(bounds[i,1], bounds[i,2], length.out = splits)
    }
  }
  argnames = formalArgs(cost)
  argnames = argnames[!argnames %in% names(list(...))] # don't include arguments passed through elipsis

  if (is.null(grid)) {
    grid = do.call('expand.grid', b)
    colnames(grid) = formalArgs(cost)[1:dim]
  }
  grid$cost = NA

  if (verbose) {
    message(' Mimimum bounds provided for ', paste(colnames(grid)[-ncol(grid)], collapse = ', '), ' are: ',
            paste(bounds[,1], collapse = ', '))
    message(' Maximum bounds provided for ', paste(colnames(grid)[-ncol(grid)], collapse = ', '), ' are: ',
            paste(bounds[,2], collapse = ', '))
  }

  ## Calculate cost function at each grid location
  best = Inf
  for (i in 1:nrow(grid)) {
    args = as.list(grid[i, 1:dim])
    names(args) = argnames[1:length(args)]
    args = c(args, list(...))

    #if (length(args) > length(formalArgs(cost))) { stop('Number of function arguments exceeds what function is expecting.') }
    grid$cost[i] = do.call(cost, args) # cost(grid[i, 1:dim])
    if (verbose & grid$cost[i] < best) {
      message(Sys.time(), ': New optimal parameter set found for n = ', n,': ', paste(grid[i,], collapse = ', '))
      best = grid$cost[i]
    }
  }

  ## Best grid location
  l = which.min(grid$cost)
  if (n == 1) {
    res = list(min = grid[l,], bounds = bounds, grid = grid, history = grid[l,], full.grid = grid)
  } else{

    ## Setup new bounding box
    loci = grid[l, 1:dim]
    bounds.new = data.frame(min = as.numeric(loci), max = as.numeric(loci))
    for (i in 1:dim) {
      bounds.new$min[i] = max(bounds$min[i], bounds.new$min[i] - progression * (bounds$max[i] - bounds$min[i]) / splits)
      bounds.new$max[i] = min(bounds$max[i], bounds.new$max[i] + progression * (bounds$max[i] - bounds$min[i]) / splits)
    }

    ## Call parameter.search recursively
    res = parameter.search(n-1, cost, ..., bounds = bounds.new, splits = splits, progression = progression, verbose = F)
    res$history = rbind(res$history, grid[l,])
    res$full.grid = rbind(res$full.grid, grid)
  }
  ## Return
  res
}

```

## Step 2: Load FRRf files

Update for your wd and folder name

```{r}

setwd("C:/Users/mlb72/OneDrive/Documents")

frrf.files = list.files('fcyl diel frrf')

frrf = load.frrf(input.dir = 'fcyl diel frrf/', file.names = frrf.files)
```

## Step 3: Remove metadata file

Only run this 1x or you will keep removing files

```{r}
# must remove TK's stamp file

length(frrf) #check length of loaded files

frrf<-frrf[1:(length(frrf)-1)] 

length(frrf)
```

# Load Match.sheet

```{r}
# Match time file

setwd("C:/Users/mlb72/OneDrive/Documents")

Fcyl.match<-read.csv('Fcyl_24hr_Diel_Match.sheet.csv')


Fcyl.match$Match.time<-as.POSIXct(as.character(Fcyl.match$Match.time))

print(Fcyl.match$Match.time)
```

## Step 2: File Matching

This matches files based on an exact match File.name column in the match.sheet.

If you want a which.closest.time matching code, let me know!

```{r}

for (i in seq_along(frrf)) {
  filename <- frrf[[i]]$File[1]
  rows <- Fcyl.match[Fcyl.match$File.name == filename, -1]
  frrf[[i]]$Label <- bind_rows(frrf[[i]]$Label, rows)
}
```

# Plot JVPII vs E

Visualize initial data

```{r}
plot_list <- list()

for (i in 1:length(frrf)) {
  E <- frrf[[i]]$A$E[1:11] # adjust to # of light steps
  JVPII <- frrf[[i]]$A$JVPII[1:11]
  Acc <- frrf[[i]]$Label$Culture.Id
  
  df <- rbind(data.frame(E, JVPII))
  
  p <- ggplot(df, aes(E, JVPII))+
    geom_point()+
    labs(title = Acc)+
    theme_minimal()
  
  plot_list[[i]] <- p
}

plot_list
```

# Calculate!

## Step 1: Alpha

First, must extract first 4 JVPII points

Can be updated if you want fewer or more.

```{r}

JVPII_line <- list()

for (i in 1:length(frrf)) {
  file <- frrf[[i]]$File[1]
  jvpii <- frrf[[i]]$A$JVPII[1:4]
  Ek <- frrf[[i]]$S$Ek[1]
  E <- frrf[[i]]$A$E[1:4]
  
  JVPII_line[[i]] <- rbind(data.frame(file, E, jvpii,Ek))
  
}
```

## Calculate Alpha

Using the first 4 JVPII points and a simple linear model

```{r}

alpha_list <- list() # empty list to store data

for (i in 1:length(JVPII_line)) {
  # df <- JVPII_line[[i]]
  JVPII <- JVPII_line[[i]]$jvpii[1:4] # JVPII
  E <- JVPII_line[[i]]$E[1:4] # E
  Ek <- JVPII_line[[i]]$Ek[1] # extracting Ek now
  file <- JVPII_line[[i]]$file # File name to bind back later
  
  mod <- lm(JVPII ~ E)
  
  alpha <- coef(mod)[2] #extract slope as alpha
  
  alpha_list[[i]] <- rbind(data.frame(file, JVPII, E, Ek, alpha))

}
```

## Calculate Pmax

Using the calculated Alpha and FRRf Ek

```{r}

pmax_list <- list()

for (i in seq_along(alpha_list)) {
  Ek <- alpha_list[[i]]$Ek[1]
  Alpha <- alpha_list[[i]]$alpha[1]
  File <- alpha_list[[i]]$file
  
  Pmax <- Alpha * Ek # equation 
  
  pmax_list[[i]] <- rbind(data.frame(File, Ek, Alpha, Pmax))
}
```

# Bind data back together

want to toss the data back into the FRRf files to keep organized

## Step 1: Extract vectors of calculated data

```{r}

## Extract data into vectors =====

Alpha <- rep(0, length(pmax_list))

for (i in 1:length(pmax_list)) {
  Alpha[[i]] <- pmax_list[[i]]$Alpha[1]
}

Pmax <- rep(0, length(pmax_list))

for (i in 1:length(pmax_list)) {
  Pmax[[i]] <- pmax_list[[i]]$Pmax[1]
}

File <- rep("a", length(pmax_list))

for (i in 1:length(pmax_list)) {
  File[[i]] <- pmax_list[[i]]$File[1]
}


## Bind calculated =====

calc.values <- rbind(data.frame(File, Alpha,
                                Pmax))
```

## Step 2: Append back into FRRf files

NOTE: This code uses the exact file names to match

```{r}
for (i in seq_along(frrf)) {
  filename <- frrf[[i]]$File[1]
  rows <- calc.values[calc.values$File == filename, -1]
  frrf[[i]]$Calculated <- bind_rows(frrf[[i]]$Calculated, rows)
}
```

# Plot

NOTE: This code uses the Culture.Id identifer from the match.sheet. Can be updated for file name or time

Acc \<- frrf[[i]]\$File or frrf[[i]]\$Datetime

```{r}
all_list <- list()

for (i in 1:length(frrf)) {
  # frf <- frrf[[i]]
  E <- frrf[[i]]$A$E[1:12]
  JVPII <- frrf[[i]]$A$JVPII[1:12]
  Ek <- frrf[[i]]$S$Ek[1]
  Alpha <- frrf[[i]]$Calculated$Alpha
  Pmax <- frrf[[i]]$Calculated$Pmax
  Acc <- frrf[[i]]$Label$Culture.Id
  
  df <- rbind(data.frame(E, JVPII, Ek, Alpha, Pmax))
  
  p <- ggplot(df, aes(E, JVPII))+
    geom_point()+
    geom_vline(xintercept = Ek, linetype = "dashed", col = "cornflowerblue")+
    geom_hline(yintercept = Pmax, linetype = "dashed", col = "tomato")+
    geom_abline(intercept = 0, slope = Alpha, linetype = "dashed", col = "slateblue2")+
    theme_minimal()+
    annotate("text", x = 30, y = 0, label = paste0(Alpha), col = "slateblue2")+
    annotate("text", x = 100, y = 0.2, label = paste0(Ek), col = "cornflowerblue")+
    annotate("text", x = 200, y = 0.25, label = paste0(Pmax), col = "tomato")+
    labs(title = Acc)
  
  all_list[[i]] <- p
}

all_list
```

# Model!

## Step 1: Separate your acclimation if needed!

This code is written specifically for subsetting specific acclimations. The new list of data is 'filtered_list[[i]]'. If you do NOT subset, you will need to update the following code from filtered_list[[i]] back to frrf[[i]]

```{r}


# Specify the Culture.ID you want to extract
target_culture_id <- "Fcyl-D-HL-100" # update this based on acclimation name

# Create an empty list to store the filtered items
filtered_list <- list()

# Loop through the original list and filter based on the target Culture.ID
for (i in seq_along(frrf)) {
  item <- frrf[[i]]
  # Print the current item's Culture.IDs
  print(paste("Item", i, "Culture.IDs:", toString(item$Label$Culture.Id)))
  if (target_culture_id %in% item$Label$Culture.Id) {
    filtered_list <- append(filtered_list, list(item))
  }
}
```

## Step 2: Summarize your calculated model parameters

From your specific filtered list

```{r}
# Extract data #####

## Alpha =====

alpha <- rep(0, length(filtered_list)) 

for (i in 1:length(filtered_list)) {
  alpha[[i]] <- filtered_list[[i]]$Calculated$Alpha
}

## Pmax =====

pmax <- rep(0, length(filtered_list))

for (i in 1:length(filtered_list)) {
  pmax[[i]] <- filtered_list[[i]]$Calculated$Pmax
}

## File (again) ======

File <- rep("a", length(filtered_list)) 

for (i in 1:length(filtered_list)) {
  File[[i]] <- filtered_list[[i]]$File
}

# Bind together #####

data <- rbind(data.frame(File, alpha, pmax))

```

## Step 3: Summarize data

## Step 4: calculate 15%

```{r}

alpha.vector <- rep(0, length(filtered_list))

pmax.vector <- rep(0, length(filtered_list))

culture.id.vector <- rep("a", length(filtered_list))

for (i in 1:length(filtered_list)) {
  alpha.vector[i] <- filtered_list[[i]]$Calculated$Alpha
}

for (i in 1:length(filtered_list)) {
  pmax.vector[i] <- filtered_list[[i]]$Calculated$Pmax
}

# for (i in 1:length(filtered_list)) {
#   culture.id.vector[i] <- filtered_list[[i]]$Calculated$culture.id.vector
# }

alpha.max <- max(alpha.vector)
a.max <- (alpha.max * 0.15) + alpha.max

alpha.min <- min(alpha.vector)
a.min <- alpha.min - (alpha.min * 0.15)

pmax.max <- max(pmax.vector)
p.max <- (pmax.max *0.15) + pmax.max

pmax.min <- min(pmax.vector)
p.min<- pmax.min- (pmax.min * 0.15)

# Print #####

print(a.min) # minimum alpha
print(a.max) # max alpha
print(p.min) #min pmax
print(p.max) # max pmax


```

# Model Platt1980

## Define model

This is updated from TBK and JR... it is now super long

```{r}

# Adjust model to fit within bounds and ignore outliers
model.Platt1980 = function(alpha, beta, Ps, E) {
  Ps * (1 - exp(-1 * alpha * E / Ps)) * exp(-beta * E / Ps)
} # base model 

ssr = function(alpha, beta, Ps, E, JVPII) {
  predicted = model.Platt1980(alpha = alpha, beta = beta, Ps = Ps, E = E)
  cost = sum((predicted - JVPII)^2, na.rm = TRUE) 
  return(cost)
} # sum of squares function 

parameter.search = function(n, cost, grid = NULL, bounds, splits = 10, progression = NULL, verbose = TRUE, ...) {
  if (verbose){
    message('Starting Parameter Search')
    message('Parameter search is an iterative grid search algorithm that seeks the parameters that minimize\nan objective cost function given a set of parameter bounds.')
  }
  
  a = Sys.time()
  if (splits <= 2) stop('splits argument must be an integer greater than or equal to 3!')
  if(is.null(progression)) {
    progression = max(1, ceiling(splits / 4))
    if (verbose) message('No Progression given, default to:\t', progression)
  }
  
  splits = round(splits)
  if (verbose) message('Number of splits set to:\t\t', splits)
  
  dim = nrow(bounds)
  b = list()
  for (i in 1:nrow(bounds)) {
    if (bounds[i,1] == bounds[i,2]) {
      b[[i]] = bounds[i,1]
    } else {
      b[[i]] = seq(bounds[i,1], bounds[i,2], length.out = splits)
    }
  }
  
  argnames = formalArgs(cost)
  argnames = argnames[!argnames %in% names(list(...))]
  
  if (is.null(grid)) {
    grid = do.call('expand.grid', b)
    colnames(grid) = formalArgs(cost)[1:dim]
  }
  
  grid$cost = NA
  best = Inf
  
  for (i in 1:nrow(grid)) {
    args = as.list(grid[i, 1:dim])
    names(args) = argnames[1:length(args)]
    args = c(args, list(...))
    grid$cost[i] = do.call(cost, args)
    
    if (verbose & grid$cost[i] < best) {
      message(Sys.time(), ': New optimal parameter set found for n = ', n,': ', paste(grid[i,], collapse = ', '))
      best = grid$cost[i]
    }
  }
  
  l = which.min(grid$cost)
  if (n == 1) {
    res = list(min = grid[l,], bounds = bounds, grid = grid, history = grid[l,], full.grid = grid)
  } else {
    loci = grid[l, 1:dim]
    bounds.new = data.frame(min = as.numeric(loci), max = as.numeric(loci))
    for (i in 1:dim) {
      bounds.new$min[i] = max(bounds$min[i], bounds.new$min[i] - progression * (bounds$max[i] - bounds$min[i]) / splits)
      bounds.new$max[i] = min(bounds$max[i], bounds.new$max[i] + progression * (bounds$max[i] - bounds$min[i]) / splits)
    }
    
    res = parameter.search(n-1, cost, ..., bounds = bounds.new, splits = splits, progression = progression, verbose = FALSE)
    res$history = rbind(res$history, grid[l,])
    res$full.grid = rbind(res$full.grid, grid)
  }
  
  return(res)
}

```

## Empty dataframe

Must have somewhere for the model to store data

```{r}
results <- data.frame(filename = character(length(filtered_list)),
                      alpha = numeric(length(filtered_list)),
                      beta = numeric(length(filtered_list)),
                      Ps = numeric(length(filtered_list)),
                      cost = numeric(length(filtered_list)),
                      stringsAsFactors = FALSE)

```

# Model!

This is computationally heavy. To reduce the load, you can reduce the splits, but it will not fit as well.

NOTE: In the bounds, your calculated a.min/p.min/a.max/p.max values have been put in

```{r include = FALSE}
for (i in 1:length(filtered_list)) {
  
  # Extract the filename from the filtered_list list (assuming filenames are stored in a named element or can be inferred)
  filename <- filtered_list[[i]]$File  # Adjust this line if filenames are stored differently
  
  # Perform the first parameter search
  fit <- parameter.search(n = 3, cost = ssr, 
                          bounds = data.frame(min = c(a.min, 0, p.min), max = c(a.max, 0.05, p.max)), 
                          splits = 10, E = filtered_list[[i]]$A$E, JVPII = filtered_list[[i]]$A$JVPII)
  
  # Check if multiple rows exist in fit$min and handle accordingly
  if (nrow(fit$min) > 1) {
    message("Multiple optimal solutions found. Selecting the first one.")
    fit$min <- fit$min[1, ]
  }
  
  resid <- abs(model.Platt1980(fit$min$alpha, fit$min$beta, fit$min$Ps, E = filtered_list[[i]]$A$E) - filtered_list[[i]]$A$JVPII)
  
  # Refit the model after removing the worst outlier
  outlier_index <- which.max(resid)
  
  fit <- parameter.search(n = 3, cost = ssr, 
                          bounds = data.frame(min = c(a.min, 0, p.min), max = c(a.max, 0.05, p.max)), 
                          splits = 20, E = filtered_list[[i]]$A$E[-outlier_index], JVPII = filtered_list[[i]]$A$JVPII[-outlier_index])
  
  # Ensure fit$min is reduced to one row before assigning
  if (nrow(fit$min) > 1) {
    message("Multiple optimal solutions found after outlier removal. Selecting the first one.")
    fit$min <- fit$min[1, ]
  }
  
  # Store the results in the data frame
  results$filename[i] <- filename
  results$alpha[i] <- fit$min$alpha
  results$beta[i] <- fit$min$beta
  results$Ps[i] <- fit$min$Ps
  results$cost[i] <- fit$min$cost
}

```

## Sum results

```{r}

print(results)

```

### Append results into frrf data

Put's back into the filtered list

```{r}
for (i in seq_along(filtered_list)) {
  Filename <- filtered_list[[i]]$File[1]
  rows <- results[results$filename == Filename, -1]
  filtered_list[[i]]$Model <- bind_rows(filtered_list[[i]]$Model, rows)
}
```

# Plot model fits with data

Note: This uses the match.sheet Culture.Id to label. Can be adjusted to something else

Ex: ID \<- filtered_list[[i]]\$File or \$Datetime

```{r}

plot_list <- list()

for (i in 1:length(filtered_list)) {
  # Extract the best-fit parameters for the i-th dataset
  alpha <- filtered_list[[i]]$Model$alpha
  beta <- filtered_list[[i]]$Model$beta
  Ps <- filtered_list[[i]]$Model$Ps
  file <- filtered_list[[i]]$File
  ID <- filtered_list[[i]]$Label$Culture.Id
  
  # Get the observed data
  observed_E <- filtered_list[[i]]$A$E
  observed_JVPII <- filtered_list[[i]]$A$JVPII
  
  # Compute the model predictions
  predicted_JVPII <- model.Platt1980(alpha, beta, Ps, observed_E)
  
  # Combine observed data and predictions into a data frame
  plot_data <- data.frame(E = observed_E,
                          Observed_JVPII = observed_JVPII,
                          Predicted_JVPII = predicted_JVPII,
                          File = file,
                          ID = ID)
  
  # Plot the observed data and model fit
  p <- ggplot(plot_data, aes(x = E)) +
    geom_point(aes(y = Observed_JVPII), color = 'cornflowerblue') +
    geom_line(aes(y = Predicted_JVPII), color = 'tomato') +
    labs(title = paste(File),
         x = "E",
         y = "JVPII") +
    theme_minimal()
  
  plot_list[[i]] <- p
}

plot_list

```

## Export

```{r}
output <- "C:/Users/mlb72/OneDrive/Documents/Rice/Lab/diurnal_paper/Diurnal_Data/Fcyl_DHL100_model_plots/"

for (i in seq_along(plot_list)) {
  plot_name <- paste0("plot_", i, ".jpg")
  ggsave(filename = file.path(output, plot_name), plot = plot_list[[i]], device = "jpeg")
}

```

# Bind back into FRRf

WORK IN PROG HERE

But generally this will use exact file names to bind model data back into your large frrf list

Caution: Running this multiple times may just append "Model" into each file to have multiple rows– so in each file, Model is added, but in files that don't match the filtered_list, the values will be 0. When they are matched, then it'll add another row of the data and keep the zeros. Aka, work in prog

```{r}

for (i in seq_along(frrf)) {
  Filename <- frrf[[i]]$File[1]
  rows <- results[results$filename == Filename, -1]
  frrf[[i]]$Model_results <- bind_rows(frrf[[i]]$Model_results, rows)
}
```
